Testing Gravity Using Type Ia Supernovae Discovered by Next Generation Wide Field Imaging Surveys

### 2019-03-08 doc/article.tex
spelling errors

A.~Slo\u{z}ar\footnotemark[19],

@@

\textbf{Endorsers:}
 \linebreak

%%% 
%\input{/Users/akim/project/AstroInstitutions/institutionAliases.tex}
% $^{1}$ \ED \\
%$^{2}$ \Durham \\
%$^{3}$ \SISSA \\
%$^{4}$ \IFPU \\
%$^{5}$ \INFN \\
%$^{6}$ \CFT \\
%$^{7}$ \LBL \\
%$^{8}$ \Pitt \\
%$^{9}$ \IFT \\
%$^{10}$ \UAM \\
%$^{11}$ \KIPAC \\
%$^{12}$ \Stanford \\
%$^{13}$ \SLAC \\
%$^{14}$ \Yale \\
%$^{15}$ \UR \\
%$^{16}$ \dunlap \\
%$^{17}$ \daa \\
%$^{18}$ \Umich \\
%$^{19}$ \JHU \\
%$^{20}$ \Port \\
%$^{21}$ \UNIPD \\
%$^{22}$ \SMU \\
%$^{23}$ \IUCAA \\
%$^{24}$ \UGTO \\
%$^{25}$ \FNAL \\
%$^{26}$ \RomaS \\
%$^{27}$ \INFNRM \\
%$^{28}$ \USC \\
%$^{29}$ \STSCI \\
%$^{30}$ \KSU \\
%$^{31}$ \StonyBrook \\
%$^{32}$ \KASSI \\
%$^{33}$ \SHAO\\
%$^{34}$ \BNL \\
%$^{35}$ \Syracuse \\
%$^{36}$ \UCB \\
%$^{37}$ \HarvardPhys \\
%$^{38}$ \NAOC \\
%$^{39}$ \UCAS \\
%

@@

Survey performance is examined in more detail by considering how $\sigma_\gamma$ in the cross-correlation analysis
changes with respect to the 
survey parameters  $\Omega$, $z_{\rm max}$, $t$, and $\sigma_M$, and also with respect to differential redshift bins
within a given survey.  Though not directly a survey parameter, we also examine changes with respect to our fiducial choice of  $k_{\rm max}$. \newline
%
%The dependence on the uncertainty in the growth index on the survey parameters is as follows:
%
{\it Solid Angle $\Omega$:}
The Fisher Matrix $F$ is  proportional to the survey solid angle $\Omega$ so $\sigma_\gamma \propto \Omega^{-1/2}$.
%
{\it Differential Redshift Bin $z$:}  Certain redshifts constrain $\gamma$ more strongly than others.  If at a given moment of a survey we had
a set of SNe~Ia from which to choose, it turns out the one with the lowest redshift would be preferred.
This is demonstrated to be the case at the end of both 2- and 10-year surveys with $z_{\rm max}=0.2$.
The left panel of Figure~\ref{dvar:fig} shows
 $|\partial \sigma_\gamma / \partial z|$, which
for both surveys monotonically decreases from $z=0.01$ out to $z=0.2$.  If we had
to sculpt the distribution, the preference would be to cut out the highest redshift bins
resulting in a decreased $z_{\rm max}$.   The optimal redshift distribution is thus the unsculpted SN-discovery distribution truncated by $z_{\rm max}$. 
\begin{figure}
\centering
\includegraphics[width=0.49\textwidth]{src/dvardz.png}
\includegraphics[width=0.49\textwidth]{src/dvardxxx.png}
\caption{Left: $|\partial \sigma_\gamma / \partial z|$  after two and ten years for a survy with limiting  depth $z_{\rm max}=0.2$. 
Right: $\sigma_\gamma^{-1}|\partial \sigma_\gamma / \partial \ln{t}|$ (red) and $\sigma_\gamma^{-1}\partial \sigma_\gamma / \partial \sigma_M$ (black) each as a function of
 $z_{\rm max}$ for two- (dashed) and ten-year (solid) surveys.
\label{dvar:fig}}
\end{figure}\newline
{\it Redshift Depth $z_{\rm max}$:}
Increasing the survey redshift depth increases the $\gamma$ precision.  The differential improvement in $\sigma_\gamma$ plateaus at
$z_{\rm max} \sim 0.2$ as seen in Figure~\ref{var:fig}. \newline
{\it Survey duration $t$; Intrinsic Magnitude Dispersion $\sigma_M$:}
An increased survey duration accumulates more supernovae, decreasing shot noise and  increasing the 
precision in $\gamma$ for all the surveys considered.
The surveys we consider have varying relative contributions of sample variance and shot noise: those that have a larger shot-noise contribution (i.e.\ 
shorter surveys and those with higher $z_{\rm max}$) benefit more from extending the survey duration, as shown
n the right-panel plot of Figure~\ref{dvar:fig} that shows $\sigma_\gamma^{-1}|\partial \sigma_\gamma / \partial \ln{t}|$ as a function of
 $z_{\rm max}$ for two- and ten-year surveys.
Like survey duration, intrinsic magnitude dispersion is related to survey performance through the shot noise and thus
has a similar relationship with $\sigma_\gamma$ as shown
in the left-panel plot of $\sigma_\gamma^{-1}\partial \sigma_\gamma/\partial \sigma_M$  of Figure~\ref{dvar:fig}.\newline
{\it Minimum length scale, maximum wavenumber $k_{\rm max}$:} There is a minimum length scale at which density and velocity distributions are reliably predicted from theory.  Changes in this scale engender  fractional changes in the $\gamma$ precision as  $\sigma_\gamma^{-1}\partial \sigma_\gamma/\partial k_{\rm max} = 0.0050$ at $k_{\rm max}=0.1h$\,Mpc$^{-1}$,
 which  is survey-independent.

@@

Combined low-redshift peculiar velocity and high-redshift RSD $fD$ measurements are highly complimentary as together they probe the
$\gamma$-dependent shape of $fD(z)$ (not just its normalization) and potential scale-dependent influence of gravitational models, since low-
and high-redshift surveys are weighted by lower and higher $k$-modes respectively.
SN~Ia peculiar velocity surveys are of the highest scientific
interest and we encourage
the community to develop aggressive surveys in the pursuit of testing  General Relativity and probing gravity.

>>>>

A.~Slo\v{z}ar\footnotemark[19],

@@

\textbf{Endorsers:}
Behzad Ansarinejad$^{1}$, 
Robert Armstrong$^{2}$, 
Jacobo Asorey$^{3}$, 
Carlo Baccigalupi$^{4,5,6}$, 
Maciej Bilicki$^{7}$, 
Julian Borrill$^{8}$, 
Elizabeth Buckley-Geer$^{9}$, 
Tamara M Davis$^{10}$, 
Kelly A. Douglass$^{11}$, 
Cora Dvorkin$^{12}$, 
Simone Ferraro$^{8}$, 
Simon Foreman$^{13}$, 
Llu\'is Galbany$^{14}$, 
Juan Garc\'ia-Bellido$^{15}$, 
Juan Garc\'ia-Bellido$^{16}$, 
Martina Gerbino$^{17}$, 
Mandeep S.S. Gill$^{18,19,20}$, 
Larry Gladney$^{21}$, 
Satya {Gontcho A Gontcho}$^{11}$, 
Julien Guy$^{8}$, 
Ren\'ee Hlo\v{z}ek$^{22,23}$, 
Dragan Huterer$^{24}$, 
Saurabh W.~Jha$^{25}$, 
Johann Cohen-Tanugi$^{26}$, 
D.\ O.\ Jones$^{27}$, 
Marc Kamionkowski$^{28}$, 
Ryan E. Keeley$^{3}$, 
Robert Kehoe$^{29}$, 
Savvas M. Koushiappas$^{30}$, 
Ely D.~Kovetz$^{31}$, 
Kazuya Koyama$^{32}$, 
Benjamin L'Huillier$^{3}$, 
Ofer Lahav$^{33}$, 
Chien-Hsiu Lee$^{34}$, 
Michele Liguori$^{35}$, 
Axel de la Macorra$^{36}$, 
Patrick McDonald$^{8}$, 
Joel Meyers$^{29}$, 
Mickael Rigault$^{37}$, 
Surhud More$^{38}$, 
Jeffrey A. Newman$^{14}$, 
Gustavo Niz$^{39}$, 
Antonella Palmese$^{9}$, 
Francesco Piacentini$^{40}$, 
Francesco Piacentni$^{40,41}$, 
Steven Rodney$^{42}$, 
Benjamin Rose$^{43}$, 
Masao Sako$^{44}$, 
Lado Samushia$^{45}$, 
Neelima Sehgal$^{46}$, 
Leonardo Senatore$^{18}$, 
Arman Shafieloo$^{3}$, 
Sara Simon$^{24}$, 
An\v{z}e Slosar$^{47}$, 
Stephanie Escoffier$^{48}$, 
Scott Watson$^{49}$, 
Martin White$^{50,8}$, 
Weishuang Xu$^{12}$, 
Gong-Bo Zhao$^{51,32}$, 
Yi Zheng$^{52}$, 
\linebreak

%%% 
\input{/Users/akim/project/AstroInstitutions/institutionAliases.tex}
 $^{1}$ \Durham \\
$^{2}$ \LLNL \\
$^{3}$ \KASSI \\
$^{4}$ \SISSA \\
$^{5}$ \IFPU \\
$^{6}$ \INFN \\
$^{7}$ \CFT \\
$^{8}$ \LBL \\
$^{9}$ \FNAL \\
$^{10}$ \Queensland \\
$^{11}$ \UR \\
$^{12}$ \HarvardPhys \\
$^{13}$ \CITA \\
$^{14}$ \Pitt \\
$^{15}$ \IFT \\
$^{16}$ \UAM \\
$^{17}$ \ANLHEP \\
$^{18}$ \KIPAC \\
$^{19}$ \Stanford \\
$^{20}$ \SLAC \\
$^{21}$ \Yale \\
$^{22}$ \dunlap \\
$^{23}$ \daa \\
$^{24}$ \Umich \\
$^{25}$ \Rutgers \\
$^{26}$ \LUPM \\
$^{27}$ \UCSC \\
$^{28}$ \JHU \\
$^{29}$ \SMU \\
$^{30}$ \Brown \\
$^{31}$ \BenGurion \\
$^{32}$ \Port \\
$^{33}$ \UCL \\
$^{34}$ \NOAO \\
$^{35}$ \UNIPD \\
$^{36}$ \IFUNAM \\
$^{37}$ \LPC \\
$^{38}$ \IUCAA \\
$^{39}$ \UGTO \\
$^{40}$ \RomaS \\
$^{41}$ \INFNRM \\
$^{42}$ \USC \\
$^{43}$ \STSCI \\
$^{44}$ \UPenn \\
$^{45}$ \KSU \\
$^{46}$ \StonyBrook \\
$^{47}$ \BNL \\
$^{48}$ \CPPM \\
$^{49}$ \Syracuse \\
$^{50}$ \UCB \\
$^{51}$ \NAOC \\
$^{52}$ \KIAS \\

@@

Survey performance is examined in more detail by considering how $\sigma_\gamma$ in the cross-correlation analysis
changes with respect to the 
survey parameters  $\Omega$, $z_{\rm max}$, $t$, and $\sigma_M$, and also with respect to differential redshift bins
within a given survey.  Though not directly a survey parameter, we also examine changes with respect to our fiducial choice of  $k_{\rm max}$. \newline
%
%The dependence on the uncertainty in the growth index on the survey parameters is as follows:
%
{\it Solid Angle $\Omega$:}
The Fisher Matrix $F$ is  proportional to the survey solid angle $\Omega$ so $\sigma_\gamma \propto \Omega^{-1/2}$.
%
{\it Differential Redshift Bin $z$:}  Certain redshifts constrain $\gamma$ more strongly than others.  If at a given moment of a survey we had
a set of SNe~Ia from which to choose, it turns out the one with the lowest redshift would be preferred.
This is demonstrated to be the case at the end of both 2- and 10-year surveys with $z_{\rm max}=0.2$.
The left panel of Figure~\ref{dvar:fig} shows
 $|\partial \sigma_\gamma / \partial z|$, which
for both surveys monotonically decreases from $z=0.01$ out to $z=0.2$.  If we had
to sculpt the distribution, the preference would be to cut out the highest redshift bins
resulting in a decreased $z_{\rm max}$.   The optimal redshift distribution is thus the unsculpted SN-discovery distribution truncated by $z_{\rm max}$. 
\begin{figure}
\centering
\includegraphics[width=0.49\textwidth]{src/dvardz.png}
\includegraphics[width=0.49\textwidth]{src/dvardxxx.png}
\caption{Left: $|\partial \sigma_\gamma / \partial z|$  after two and ten years for a survey with limiting  depth $z_{\rm max}=0.2$. 
Right: $\sigma_\gamma^{-1}|\partial \sigma_\gamma / \partial \ln{t}|$ (red) and $\sigma_\gamma^{-1}\partial \sigma_\gamma / \partial \sigma_M$ (black) each as a function of
 $z_{\rm max}$ for two- (dashed) and ten-year (solid) surveys.
\label{dvar:fig}}
\end{figure}\newline
{\it Redshift Depth $z_{\rm max}$:}
Increasing the survey redshift depth increases the $\gamma$ precision.  The differential improvement in $\sigma_\gamma$ plateaus at
$z_{\rm max} \sim 0.2$ as seen in Figure~\ref{var:fig}. \newline
{\it Survey duration $t$; Intrinsic Magnitude Dispersion $\sigma_M$:}
An increased survey duration accumulates more supernovae, decreasing shot noise and  increasing the 
precision in $\gamma$ for all the surveys considered.
The surveys we consider have varying relative contributions of sample variance and shot noise: those that have a larger shot-noise contribution (i.e.\ 
shorter surveys and those with higher $z_{\rm max}$) benefit more from extending the survey duration, as shown
n the right-panel plot of Figure~\ref{dvar:fig} that shows $\sigma_\gamma^{-1}|\partial \sigma_\gamma / \partial \ln{t}|$ as a function of
 $z_{\rm max}$ for two- and ten-year surveys.
Like survey duration, intrinsic magnitude dispersion is related to survey performance through the shot noise and thus
has a similar relationship with $\sigma_\gamma$ as shown
in the left-panel plot of $\sigma_\gamma^{-1}\partial \sigma_\gamma/\partial \sigma_M$  of Figure~\ref{dvar:fig}.\newline
{\it Minimum length scale, maximum wavenumber $k_{\rm max}$:} There is a minimum length scale at which density and velocity distributions are reliably predicted from theory.  Changes in this scale engender  fractional changes in the $\gamma$ precision as  $\sigma_\gamma^{-1}\partial \sigma_\gamma/\partial k_{\rm max} = 0.0050$ at $k_{\rm max}=0.1h$\,Mpc$^{-1}$,
 which  is survey-independent.

@@

Combined low-redshift peculiar velocity and high-redshift RSD $fD$ measurements are highly complementary as together they probe the
$\gamma$-dependent shape of $fD(z)$ (not just its normalization) and potential scale-dependent influence of gravitational models, since low-
and high-redshift surveys are weighted by lower and higher $k$-modes respectively.
SN~Ia peculiar velocity surveys are of the highest scientific
interest and we encourage
the community to develop aggressive surveys in the pursuit of testing  General Relativity and probing gravity.
